---
title: Feb, 28, 2016 -In-Class Project
date: '2017-03-05'
slug: feb-28-2016-in-class-project
---

##1
```{r}
ckm_nodes<-read.csv("~/Desktop/Brown_Course/2560/ckm_nodes.csv",header = TRUE)
dim(ckm_nodes)
colnames(ckm_nodes)
```
There are 246 rows and 13 columns in this ckm_nodes data file and there are columns named city and adoption_date.

##2
```{r}
table(ckm_nodes$adoption_date)
```

There are 16 doctors never prescribed. There are 121 missing records. 
```{r}
length(which(is.na(ckm_nodes$adoption_date)))
#summary(ckm_nodes$adoption_date)
```

##3
A vector called index includes all index of doctor, and the length is 125. 
```{r}
index<-which(!is.na(ckm_nodes$adoption_date))
length(index)
cleaned_nodes<-ckm_nodes[index,]
```

##4
```{r}
adopters<-function(month,not.yet=FALSE){
  if(not.yet==FALSE){ 
  return(as.vector(cleaned_nodes$adoption_date==month))
  } else {
  return(as.vector(cleaned_nodes$adoption_date>month))  
  }
}
adopters(2)
sum(adopters(2))
sum(adopters(month=14,not.yet = TRUE))
```

##5
```{r}
ckm_network<-read.table("~/Desktop/Brown_Course/2560/ckm_network.dat",header= FALSE, sep="")
clean_networks<-ckm_network[index,index]
dim(clean_networks)
```

##6
```{r}
contacts_number<-apply(clean_networks, 1, sum)
contacts_number[41]
```

###Part 2

##7
```{r}
count_peer_pressure<-function(index,month){
  sum(cleaned_nodes[which(clean_networks[index]==1),2]<=month)
}
count_peer_pressure(37,5)
```


```{r}
###
prop_peer_pressure<-function(index,month){
  if(contacts_number[index]==0){
    return(NaN)
  } else {
    return(count_peer_pressure(index,month)/contacts_number[index])
  }
}

prop_peer_pressure(37,5)
prop_peer_pressure(102,4)
```

##8

```{r}
average<-function(month){
  vector<-rep(NA,2)
  #began prescribing in that month
  began<-which(adopters(month,not.yet =FALSE)==TRUE) #docs who began prescribing
  began<-as.matrix(began)
  proportion_1<-apply(began,1,prop_peer_pressure,month=month)
  #after prescribing in that month
  after<-which(adopters(month,not.yet = TRUE))
  after<-as.matrix(as.numeric(after))
  proportion_2<-apply(after,1,prop_peer_pressure,month=month)
  vector[1]<-mean(proportion_1,na.rm=T)
  vector[2]<-mean(proportion_2,na.rm=T)
  return(vector)
}

average(1)
```


b
```{r}
month<-c(1:17)
month<-as.matrix(month)
average_month<-apply(month,1,average)
average_month_1<-average_month[1,]
average_month_2<-average_month[2,]

plot(month,average_month_1,main="Average Proportion Over Time",xlab="Month",ylab="Average Proportion",col="green",type="o",xaxt="n",yaxt="n")
axis(1,at=seq(1,17,1),labels = T)
axis(2,at=seq(0,1,0.1),labels = T)
points(average_month_2,col="red",type="o")
legend("topleft",c("First Proportion","Second Proportion"),col=c("green","red"),lty=c(1,1),bty="n")
```


```{r}
#the difference of two proportions in 8a
proportions<-apply(month,1,average)
proportions<-t(proportions)
boxplot(proportions,main="Boxplot of Two Average Proportions")
```

The doctors who adopt in a given month sometimes don't have more contacts who are already prescribing than the non-adopters. 