---
title: March-13-2017-Pre-Class
date: '2017-03-20'
slug: march-13-2017-pre-class
---


###1.a

When a gambler makes a bet of $100 on a fair game, the result of this game follow bernoulli distribution with p=0.5. When we simulate the outcome at most 5000 iteration then the outcome follows a binomial distribution with n=5000, p=0.5. 

```{r}
set.seed(2560)
n<-5000
inital<-1000
dur<-rep(NA,n)
x<-inital
d<-0

for (j in 1:n){
  x<-inital
  d<-0
for (i in 1:n){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(0.5,0.5))
d<-i
}else{break}
dur[j]<-d
}}

dur<-as.vector(dur)
length1a<-length(which(dur<=100))
prob1a<-length1a/n
```

The probability that get busted by the time when we have placed one hundredth bet is 31.34%.

###1.b
```{r}
length1b<-length(which(dur<=500))
prob1b<-length1b/n
prob1b
```

The probability that get busted by the time when we have placed one hundredth bet is 65.32%

###1.c
```{r}
dur.1c<-dur[!dur==5000]
mean.time<-mean(dur.1c)
mean.time
```

The mean time that go bust given go bust within the first 5000 hands is 506.204.

###1.d
```{r}
set.seed(2560)
bankroll.1d<-rep(NA,n)

for (j in 1:n){
  x<-inital
for (i in 1:100){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(0.5,0.5))
}}
bankroll.1d[j]<-x
}

mean1d<-mean(bankroll.1d)
var1d<-var(bankroll.1d)
```

The mean of bankroll after 100 hands is `r mean1d`, and the variance of bankroll is `r var1d`. 

###1.e
```{r}
set.seed(2560)
bankroll.1e<-rep(NA,n)

for (j in 1:n){
  x<-inital
for (i in 1:500){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(0.5,0.5))
}}
bankroll.1e[j]<-x
}

mean1e<-mean(bankroll.1e,na.rm=T)
mean1e
var1e<-var(bankroll.1e)
var1e
```

The mean of bankroll after 500 hands is `r mean1e `, and the variance of bankroll after 500 hands is `r var1e`.

###2.a
```{r}
set.seed(2560)
p<-18/38
dur2<-rep(NA,n)

for (j in 1:n){
  x<-inital
  d<-0
for (i in 1:n){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(1-p,p))
d<-i
}else{break()}}
dur2[j]<-d
}

prob2a<-length(which(dur2<=100))/n
prob2a
```

The probability that get busted by the time when we have placed one hundredth bet is `r prob2a`.


###2.b
```{r}
prob2b<-length(which(dur2<=500))/n
```

The probability that get busted by the time when we have placed five hundredth bet is 91.9%.

###2.c
```{r}
dur2.c<-dur2[!dur2==5000]
mean.2c<-mean(dur2.c)
```

The mean time that go bust given go bust within the first 5000 hands is 186.622


###2.d
```{r}
set.seed(2560)
bankroll.2d<-rep(NA,n)

for (j in 1:n){
  x<-inital
for (i in 1:100){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(1-p,p))
}}
bankroll.2d[j]<-x
}

mean2d<-mean(bankroll.2d)
var2d<-var(bankroll.2d)

mean2d
var2d
```

The mean of bankroll after 100 hands is `r mean2d`, and the variance of bankroll is `r var2d`.

###2.e
```{r}
set.seed(2560)
bankroll.2e<-rep(NA,n)

for (j in 1:n){
  x<-inital
for (i in 1:500){
if(x!=0){
x<-x+100*sample(c(-1,1),1,replace=TRUE,prob=c(1-p,p))
}}
bankroll.2e[j]<-x
}

mean2e<-mean(bankroll.2e)
var2e<-var(bankroll.2e)

mean2e
var2e
```

The mean of bankroll after 500 hands is `r mean2e`, and the variance of bankroll is `r var2e`.


###3.a
```{r}
ini.win<-0.48
p3<-ini.win
prob3a<-rep(NA,100000)
return<-rep(NA,100000)
expected.return<-rep(NA,100)
set.seed(2560)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))
return[i+1]<-return[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))
#first.return<-100*first
if (p3<1){
  if(first==1){
    p3<-p3+0.01
  }else{p3<-ini.win}
}else{p3=1}
prob3a[i]<-p3
}
expected.return[j]<-return[100000] 
  }
mean.3a<-mean(expected.return)
```

It's not a fair game, the more hands a gambler play the more money he will lose on this game. 


###3.b
Suppose the probability of winning on first hand is 51%, and the rest probabilities are the same as previous. When the starting probability is 49% the game is becoming fair.
```{r,eval=FALSE}
p4<-0.51
return2<-rep(NA,100000)
expected.return2<-rep(NA,100)
prob3b<-rep(NA,100000)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p4,p4))
#return2[i+1]<-return2[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p4,p4))
if (p4<1){
  if(first==1){
    p4<-p4+0.01
  }else{p4=0.51}
}else{p4=1}
prob3b[i]<-p4
return2[1]<-100*first
return2[i+1]<-return2[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p4,p4))}
expected.return2[j]<-return2[100000] 
}
mean.er2<-mean(expected.return2)


#try set the starting probability to 50%
p5<-0.5
return3<-rep(NA,100000)
expected.return3<-rep(NA,100)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p5,p5))
#return2[i+1]<-return2[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p4,p4))
if (p5<1){
  if(first==1){
    p5<-p5+0.01
  }else{p5=0.5}
}else{p5=1}
return3[1]<-100*first
return3[i+1]<-return3[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p5,p5))}
expected.return3[j]<-return3[100000] 
}

mean.er3<-mean(expected.return3)
```

```{r}
#try set the starting probability to 49%
p6<-0.49
return4<-rep(NA,100000)
expected.return4<-rep(NA,100)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p6,p6))
#return2[i+1]<-return2[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p4,p4))
if (p6<1){
  if(first==1){
    p6<-p6+0.01
  }else{p6=0.49}
}else{p6=1}
return4[1]<-100*first
return4[i+1]<-return4[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p6,p6))}
expected.return4[j]<-return4[100000] 
}

mean.er4<-mean(expected.return4)
mean.er4
```

 

###3.c

When set the increment probability at 2%, this game is becoming a fair game. 
```{r}
#set the increment probability to 1.5%
set.seed(2560)
p3<-0.48
return5<-rep(NA,100000)
expected.return5<-rep(NA,100)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))
if (p3<0.985){
  if(first==1){
    p3<-p3+0.015
  }else{p3<-0.48}
}else{p3==1}
return5[1]<-100*first
return5[i+1]<-return5[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))}
expected.return5[j]<-return5[100000] 
}
mean(expected.return5)

#set the increment probability to 2%
p3<-0.48
return6<-rep(NA,100000)
expected.return6<-rep(NA,100)
set.seed(2560)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))
if (p3<0.98){
  if(first==1){
    p3<-p3+0.02
  }else{p3<-0.48}
}else{p3==1}
return6[1]<-100*first
return6[i+1]<-return6[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))}
expected.return6[j]<-return6[100000] 
}

mean(expected.return6)


#set the increment probability to 1.55%

p3<-0.48
return7<-rep(NA,100000)
expected.return7<-rep(NA,100)
set.seed(2560)

for (j in 1:100){
for (i in 1:100000){
first<-sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))
if (first==1){
  if(p3<0.9845){
    p3<-p3+0.0155
  } else {p3=1}
}else{p3=0.48}
 return7[1]<-100*first
 return7[i+1]<-return7[i]+100*sample(c(-1,1),1,replace = TRUE,prob=c(1-p3,p3))}
  expected.return7[j]<-return7[100000]
  }
mean(expected.return7)
```


###4
```{r}
set.seed(2560)
B<-1000
d1<-as.matrix(expected.return4)
d1<-data.frame(d1)
mean1<-rep(NA,100)
for (i in 1:B){
  n<-nrow(d1)
  index1<-sample(1:n,size=n,replace=TRUE)
  boot.data1<-d1[index1,]
  mean1[i]<-mean(boot.data1)
  }
var4.1<-var(mean1)


set.seed(2560)
d2<-as.matrix(expected.return6)
d2<-data.frame(d2)
mean2<-rep(NA,100)
for (i in 1:B){
  n<-nrow(d2)
  index2<-sample(1:n,size=n,replace=TRUE)
  boot.data2<-d2[index2,]
  mean2[i]<-mean(boot.data2)
}
var4.2<-var(mean2)
```

The variance of second game mean of return is 2614 and the variance of first game mean of return is 10228630. In general, the second game has a smaller variance in returns.